---
title: "Webscraping - Assignment 2"
author: "AttilaSerfozo"
date: '2020.12.14 '
output:
  prettydoc::html_pretty:
    theme: cayman
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}

rm(list=ls())
library(prettydoc)
library(data.table)
library(rvest)
library(tidyverse)

data_out <- "C:/Users/Attila/Documents/CEU/Coding_Webscraping/Assignment2-hasznaltauto/"
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
In this project I collected data from the catalog of the most used Hungarian used car website hasznaltauto.hu. During the exercise I collect all the available car brands which is presented in the website's catalog then I create a function to get all information for one car and another function to generate the link of cars for the selected brand. In the end I finish with a function in which the user needs to type in a brand from the brand list, located in the data folder. As there are thousands of observations in case of some brands, and the running of the query can last long I tried the exercise with Bentley (63 observations), Maserati (138 observations), Alfa-Romeo (854 observations) and Honda (1442 observations) as they took a reasonable amount of time.

## Get list of car brands
The list contains the name of the brands in the format in which they need to be inserted into the get_car_data function. The list can be found in the data folder.

```{r echo=TRUE}
main_page <- 'https://katalogus.hasznaltauto.hu/'
t <- read_html(main_page)
brands <-
  t %>% 
  html_nodes('.nemlatszik') %>%
  html_text()

# Cleaning brands
brands <- brands[2]
brands <- gsub(' ', '_', trimws(gsub('\n', ',', trimws(gsub('\t', '', trimws(brands), fixed = T)), fixed = T)), fixed = T)
brands <- strsplit(brands,",")[[1]]
brands <- tolower(brands)
brands <- brands[2:107]

write.csv(brands,paste0(data_out,"data/available_brands.csv"))
```

## Function for getting data of one car
This function collects the name, link and all the important data of a brands' cars.
```{r echo=TRUE}

my_link <- 'https://katalogus.hasznaltauto.hu/abarth/124_spider_1.4_multiair_t-107786'
get_one_car <- function(my_link) {
  
  t2 <- read_html(my_link)
  
  specification_list <- list()
  
  # Collect name of car
  titles <-
    t2 %>% 
    html_nodes('h1') %>%
    html_text()
  # Collect link of car
  link <- my_link
  
  # Add name and link to the list
  specification_list [['Név']] <- titles
  specification_list [['Link']] <- link
  
  # Collect car data
  category <- t2 %>%  html_nodes('.w250') %>%  html_text()
  values <- t2 %>% html_nodes('.w250+ td') %>%  html_text()
  # Append them to the list
  if (length(category) == length(values)) {
    for (key_id in 1:length(values)) {
      #print(key_id) 
      specification_list[[ category[key_id] ]] <- values[key_id]
    }
    
  }
  return(specification_list)
}

```

## Function for getting car data of the selected brand
This function generates the links of the selected brands' cars available in the catalog.
After generating the links the function combine them with the get_one_car function and gathers all their important properties.

```{r echo=TRUE}
get_car_data <- function(brand) {
  #brand <- 'bentley'
  
  # Find last page of the brand car list
  x <- read_html(paste0('https://katalogus.hasznaltauto.hu/',brand))
  last_page <-
    x %>% 
    html_nodes('.utolso a') %>%
    html_attr('href')
  
  if(length(last_page) == 0) { # If there is no jump to last page button ~ try maserati
    if (length(x %>% 
        html_nodes('.oldalszamozas .oldalszam') %>%
        html_text()) == 0) {   # If there is only 1 page ~ try bentley
      last_page <- 1
    }else{
    last_page <-
      x %>% 
      html_nodes('.oldalszamozas .oldalszam') %>%
      html_text()
    last_page <- as.numeric(tail(last_page, n=1))
    }
  }else{                       # If there is a jump to last page button ~ try honda
    last_page <- as.numeric(gsub("[^0-9]","",last_page ) )
  }
  
  # Generate pagesand car links
  pages <- paste0('https://katalogus.hasznaltauto.hu/',brand,'/page', 1:last_page)
  
  car_links <- NULL
  for (i in 1:length(pages)) {
    
    p <- read_html(pages[i])
    
    car_links <- c(car_links,
                   p %>% 
                     html_nodes('.hasonlit-jelolgeto a') %>%
                     html_attr('href')
    )
  }
  
  df <- rbindlist(lapply(car_links, get_one_car), fill = T)
  return(df)
  
}
```

# Test the function to download some data
In case of running the function be aware that some cars have more than one thousand items in the catalog, thus sometimes it requires a lot of time to download their data.
```{r echo=TRUE}
car_data1 <- get_car_data('bentley')
write.csv(car_data1,paste0(data_out,"data/raw/bentley-catalog.csv"))
#
# car_data2 <- get_car_data('maserati')
# write.csv(car_data2,paste0(data_out,"data/raw/maserati-catalog.csv"))
# 
# car_data3 <- get_car_data('alfa_romeo')
# write.csv(car_data3,paste0(data_out,"data/raw/alfa_romeo-catalog.csv"))
# 
# car_data4 <- get_car_data('honda')
# write.csv(car_data4,paste0(data_out,"data/raw/honda-catalog.csv"))
```

## Data Cleaning and exploration of distribution of variables
In the catalog_hasznaltauto-clean_data.R you can find the process of cleaning the scraped raw data file.
Please write the name of the selected brand in the "selected_brand" variable to write out the cleaned data.

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width='50%'}

#########################################
# Please add downloaded brand here
selected_brand <- 'alfa_romeo'
#########################################

data_in <- "C:/Users/Attila/Documents/CEU/Coding_Webscraping/Assignment2-hasznaltauto/data/"
car_data <- read.csv(paste0(data_in,"raw/",selected_brand,"-catalog.csv"))

car_data_clean <- separate(car_data, Maximális.teljesítmény, "," ,
                    into = c('Maximális.teljesítmény.kW', 'Maximális.teljesítmény.LE'))
car_data_clean <- 
  car_data_clean %>%
  mutate ( "Gyorsulás.0.ról.100.km.h.ra" = gsub(",", ".", car_data_clean$Gyorsulás.0.ról.100.km.h.ra),
           "Vegyes.fogyasztás" = gsub(",", ".", car_data_clean$Vegyes.fogyasztás))

car_data_clean <- 
  car_data_clean %>% 
  transmute(
    'ID' = X,
    'Név' = Név,
    'Link' = Link,
    'Kategória' = Kategória,
    'Kivitel' = Kivitel,
    #'Gyártási.idoszak' = Gyártási.időszak,
    'Üzemanyag' = Üzemanyag,
    'Újkori.ára.(mHUF)' = as.numeric(gsub("[^0-9]","",Újkori.ára) )/1000000,
    'Hengerek.száma' = as.numeric(gsub("[^0-9]","",Hengerek.száma) ),
    'Maximális.teljesítmény.(kW)' = as.numeric(gsub("[^0-9]","",Maximális.teljesítmény.kW) ),
    'Maximális.teljesítmény.(LE)' = as.numeric(gsub("[^0-9]","",Maximális.teljesítmény.LE) ),
    'Végsebesség.(km/h)' = as.numeric(gsub("[^0-9]","",Végsebesség) ),
    'Gyorsulás.(s)' = as.numeric(gsub("[^0-9\\.]","",car_data_clean$Gyorsulás.0.ról.100.km.h.ra) ),
    'CO2.kibocsátás.(g/km)' = as.numeric(gsub("[^0-9]","",CO2.kibocsátás) ),
    'Vegyes.fogyasztás.(l)' = as.numeric(gsub("[^0-9\\.]","",Vegyes.fogyasztás) ),
    'Össztömeg.(kg)' = as.numeric(gsub("[^0-9]","",Össztömeg) ),
    'Szélesség.(mm)' = as.numeric(gsub("[^0-9]","",Szélesség) ),
    'Hosszúság.(mm)' = as.numeric(gsub("[^0-9]","",Hosszúság) ),
    'Magasság.(mm)' = as.numeric(gsub("[^0-9]","",Magasság) ),
    'Ajtók.száma' = as.numeric(gsub("[^0-9]","",Ajtók.száma) ),
    'Szállítható.személyek.száma' = as.numeric(gsub("[^0-9]","",Szállítható.személyek.száma) )
  )

data_out <- "C:/Users/Attila/Documents/CEU/Coding_Webscraping/Assignment2-hasznaltauto/data/"
write.csv(car_data_clean,paste0(data_out,"clean/",selected_brand,"-catalog.csv"))

# Showing distribution of variables

ggplot( data = car_data_clean , aes( x = `Újkori.ára.(mHUF)` ) )+
  geom_histogram( binwidth =2, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 2, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Price in million HUF",y="Absolute Frequency", title="Distribution of car prices with 2m HUF bins")

ggplot( data = car_data_clean , aes( x = `Kategória` ) )+
  geom_bar( fill= "navyblue",col="black", alpha=0.7) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(x="Classes",y="Absolute Frequency", title="Distribution of cars between categories")

ggplot( data = car_data_clean , aes( x = `Kivitel` ) )+
  geom_bar( fill= "navyblue",col="black", alpha=0.7) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(x="Types",y="Absolute Frequency", title="Distribution of cars between types")


ggplot( data = car_data_clean , aes( x = `Üzemanyag` ) )+
  geom_bar( fill= "navyblue",col="black", alpha=0.7) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(x="Fuel types",y="Absolute Frequency", title="Distribution of cars between fuel types")

ggplot( data = car_data_clean , aes( x = `Hengerek.száma` ) )+
  geom_histogram( binwidth =1, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 1, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Number of cylinders",y="Absolute Frequency", title="Distribution of Number of cylinders")

ggplot( data = car_data_clean , aes( x = `Maximális.teljesítmény.(LE)` ) )+
  geom_histogram( binwidth =25, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 25, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Performance in horsepower",y="Absolute Frequency", title="Distribution of strength of cars with 25 horsepower bins")

ggplot( data = car_data_clean , aes( x = `Végsebesség.(km/h)` ) )+
  geom_histogram( binwidth =10, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 10, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Max speed in km/h",y="Absolute Frequency", title="Distribution of max speed of cars with 10 km/h bins")

ggplot( data = car_data_clean , aes( x = `Gyorsulás.(s)` ) )+
  geom_histogram( binwidth =0.5, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 0.5, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Acceleration in seconds",y="Absolute Frequency", title="Distribution of acceleration of cars with 0.5s bins")

ggplot( data = car_data_clean , aes( x = `CO2.kibocsátás.(g/km)` ) )+
  geom_histogram( binwidth =20, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 20, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="CO2 emission in g/km",y="Absolute Frequency", title="Distribution of CO2 car emissions with 20 g/km bins")

ggplot( data = car_data_clean , aes( x = `Vegyes.fogyasztás.(l)` ) )+
  geom_histogram( binwidth =1, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 1, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Mixed fuel consumption in litres",y="Absolute Frequency", title="Distribution of mixed fuel consumtion with 1l bins")

ggplot( data = car_data_clean , aes( x = `Ajtók.száma` ) )+
  geom_histogram( binwidth =1, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 1, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Number of doors",y="Absolute Frequency", title="Distribution of number of doors")

ggplot( data = car_data_clean , aes( x = `Szállítható.személyek.száma` ) )+
  geom_histogram( binwidth =1, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 1, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Carried passengers",y="Absolute Frequency", title="Distribution of carried passengers")

ggplot( data = car_data_clean , aes( x = `Össztömeg.(kg)` ) )+
  geom_histogram( binwidth =100, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 100, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Weight in kg",y="Absolute Frequency", title="Distribution of weight with 100 kg bins")

ggplot( data = car_data_clean , aes( x = `Szélesség.(mm)` ) )+
  geom_histogram( binwidth =50, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 50, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Width in mm",y="Absolute Frequency", title="Distribution of width with 5 cm bins")

ggplot( data = car_data_clean , aes( x = `Hosszúság.(mm)` ) )+
  geom_histogram( binwidth =50, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 50, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Length in mm",y="Absolute Frequency", title="Distribution of length with 5 cm bins")

ggplot( data = car_data_clean , aes( x = `Magasság.(mm)` ) )+
  geom_histogram( binwidth =50, fill= "navyblue",col="black", alpha=0.7) +
  stat_bin(geom = "text", binwidth = 50, 
           aes(label = ifelse(..count.. > 0, ..count.., "")), vjust = -0.5)+
  labs(x="Height in mm",y="Absolute Frequency", title="Distribution of height with 5 cm bins")


```